% ************************** Thesis Acknowledgements **************************

\begin{acknowledgements}      

  First of all, I would like to express my deepest thanks to my supervisor, Dr. Vitaly Kudryavtsev. I could not have produced this work without your ever watchful guidance and support. It has been a truly wonderful experience working with you for the last four and a half years. \\
  
  A huge thanks must also go to Dr. Michelle Stancari, Dr. Tingjun Yang, and Dr. Tom Junk, who supervised me during my attachment at Fermilab. I could not have asked for more friendly, knowledgeable and passionate people to be in collaboration with, and if I can become the half the physicists that any of you are, I would be immensely proud. I would also like to thank every single member of the dedicated team of people who worked on the 35 ton, you all contributed to my development as a physicist. A special mention must of course go to Michael Wallbank, who I have spent the majority of my PhD living with and sitting next to, and whose laugh will forever be etched in my psyche. Concerning Fermilab, it is impossible to list all of the amazing (and truly interesting) people that I met there, though every single one of them made my stay at Fermilab two of the best years of my life. I look forward to the next four years being as memorable as the last two! \\

  It would be impossible to not thank everyone in the Particle Physics group of Sheffield, whose sometimes constant distractions only made to make living Sheffield more enjoyable. Special thanks must go to those people that I shared an office with, Martin Richardson, Andrew Scarff, Matthew Thiesse, David Woodward, Anthony Ezeribe, Patrick Stowell, Dr. Nicola McConkey, Dr. Celeste and Liam. \\

  Finally, it goes without saying that none of this would have been possible without the fantastic support that I receive from my entire family. I wouldn't swap their feigning of interest and sarcastic comments about Sheldon for anything. It is immeasurably valuable to have a best friend for a sister, a bed of support for a mother, a rock for a nan, and a Pete for a ``Pete''. None of this would have been possible without each and every one of you. \\

\end{acknowledgements}
